The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-04-03 manuscript/manuscript.tex
Update manuscript.tex

We also compare the histogram of the inferred \Reff\ and \sersic\ n to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value. We perform the Kolmogorov?Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively. We thus conclude that the host galaxies of our AGN are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.

@@

XD and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.

>>>>

We also compare the histogram of the inferred \Reff\ and \sersic\ n to the inactive galaxies in Figure~\ref{fig:hist_rn}, where there is no significant difference between their distribution and median value. We perform the Kolmogorov-Smirnov test to interpret the p-value as 0.42 and 0.04 for \Reff\ and $n$, respectively. We thus conclude that the host galaxies of our AGN are representative of the overall population of galaxies at comparable luminosity and stellar mass at the same redshift.

@@

XD, SB and TT acknowledge support by the Packard Foundation through a Packard Research fellowship to TT.
